### 2010-09-21 Documentation/part1.tex
JK - Fixed bug in glb_likelihood (true and fitted rates exchanged)
Revert "meeting-URL corrected. -ML"
This reverts commit 7f96a80099a797c54ea125beeff5e7fdc61f7332.

the Poisson distribution, while the terms in the second line are penalties

@@

 \hspace*{0.5cm} /* Add oscillation parameter priors */ \\
  \hspace*{0.5cm}  for(i=0;i<6;i++) \\
  \hspace*{0.5cm} if(glbGetProjectionFlag(p,i)==GLB\_FREE) \\
  \hspace*{0.5cm} \{ \\
  \hspace*{1cm} fitvalue=glbGetOscParams(in,i); \\
  \hspace*{1cm} centralvalue=glbGetOscParams(central\_values,i); \\
  \hspace*{1cm} inputerror=glbGetOscParams(input\_errors,i); \\
  \hspace*{1cm} if(inputerror>1e-12) 
  \hspace*{1cm} \{ \\
  \hspace*{1.5cm} if(i==GLB\_THETA\_12) /* Prior on $\sin^2 \theta_{12}$ */ \\ 
\hspace*{2.0cm} pv+=square((startvalue-square(sin(fitvalue)))/inputerror);\\ 
  \hspace*{1.5cm} else \\ 
  \hspace*{2.0cm}  pv+=square((startvalue-fitvalue)/inputerror); \\
  \hspace*{1cm} \} \\
  \hspace*{0.5cm} \}

>>>>

the Gauss distribution, while the terms in the second line are penalties

@@

  \hspace*{0.5cm} /* Add oscillation parameter priors */ \\
  \hspace*{0.5cm}  for(i=0;i<6;i++) \\
  \hspace*{0.5cm} if(glbGetProjectionFlag(p,i)==GLB\_FREE) \\
  \hspace*{0.5cm} \{ \\
  \hspace*{1cm} fitvalue=glbGetOscParams(in,i); \\
  \hspace*{1cm} centralvalue=glbGetOscParams(central\_values,i); \\
  \hspace*{1cm} inputerror=glbGetOscParams(input\_errors,i); \\
  \hspace*{1cm} if(inputerror>1e-12) 
  \hspace*{1cm} \{ \\
  \hspace*{1.5cm} if(i==GLB\_THETA\_12) /* Prior on $\sin^2 \theta_{12}$ */ \\ 
  \hspace*{2.0cm} pv+=square((centralvalue-square(sin(fitvalue)))/inputerror);\\
  \hspace*{1.5cm} else \\ 
  \hspace*{2.0cm}  pv+=square((centralvalue-fitvalue)/inputerror); \\
  \hspace*{1cm} \} \\
  \hspace*{0.5cm} \}

### 2010-09-21 Documentation/tutorials/norm.tex
Revert "meeting-URL corrected. -ML"
This reverts commit 7f96a80099a797c54ea125beeff5e7fdc61f7332.

\begin{abstract}
A common issue with \GLOBES\ is confusion about the proper units for
the input flux files for use in \AEDL\ experiment descriptions. 
\end{abstract}

@@

In understanding how one still can figure out what the correct units
are for each case, it is a good starting point to look at what
\GLOBES\ does with the input files. The cross section in the file is given as
differential cross section divided by energy $x=\sigma/E$, and the flux file
gives $f$. The differential number of events per GeV $n$ as computed in
\GLOBES\ without oscillation and efficiencies is given by
\begin{eqnarray}
n &=& 5.20034\times x\times E\times f\times\\
&&\mathtt{@norm}\times\mathtt{@power}\times\mathtt{@stored\_muons}\times\mathtt{@time}\times\mathtt{\$target\_mass}\times(\mathtt{\$baseline})^{-2}\nonumber
\end{eqnarray}
 Beware: $5.2\ldots$ is a undocumented fudge factor!

@@

\begin{eqnarray}
\mathtt{@norm}=\frac{1}{5.20034}\left(\frac{\mathrm{GeV}}{\Delta
      E}\right)
\left(\frac{\mathrm{cm}^2}{A}\right)\left(\frac{L}{\mathrm{km}}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}_u}{\mathcal{L}}\right)
\end{eqnarray}
where the $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity and $\mathcal{L}_u$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual:

>>>>

\begin{abstract}
A common issue with \GLOBES\ is confusion about the proper units for
the input flux files for use in \AEDL\ experiment descriptions. This
version describes globes versions 3.0 and later.
\end{abstract}

@@

In understanding how one still can figure out what the correct units
are for each case, it is a good starting point to look at what
\GLOBES\ does with the input files. The cross section in the file is given as
differential cross section divided by energy $x=\sigma/E$, and the flux file
gives $f$. The differential number of events per GeV $n$ as computed in
\GLOBES\ without oscillation and efficiencies is given by
\begin{eqnarray}
n &=&  x\times E\times f\times\\
&&\mathtt{@norm}\times\mathtt{@power}\times\mathtt{@stored\_muons}\times\mathtt{@time}\times\mathtt{\$target\_mass}\times(\mathtt{\$baseline})^{-2}\nonumber
\end{eqnarray}

@@

\begin{eqnarray}
\mathtt{@norm}=\left(\frac{\mathrm{GeV}}{\Delta
      E}\right)
\left(\frac{\mathrm{cm}^2}{A}\right)\left(\frac{L}{\mathrm{km}}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}_u}{\mathcal{L}}\right)
\end{eqnarray}
where the $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity and $\mathcal{L}_u$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual:
